### 2020-04-29 Articlebackup.tex
Corregir

\newcommand{\cc}{\mathfrak{c}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Hc}{\mathcal{H}}
\newcommand{\Lan}{\mathcal{L}}
\newcommand{\Ln}{\lim\limits_{n\to \infty}}
\newcommand{\clist}{\mathfrak{c}_{1}, \cdots, \mathfrak{c}_m}
\newcommand{\morph}[1]{\simeq_#1}
\newcommand{\vlst}[2]{#1_1,\dots, #1_{#2}}
\newcommand{\gnp}{G(n,\beta_1/n^{a_1-1}, \dots,\beta_l/n^{a_l-1})}
\newcommand{\overbar}[1]{\mkern 1.5mu\overline{\mkern-1.5mu#1\mkern-1.5mu}\mkern 1.5mu}
\newcommand{\ehr}{\textsc{Ehr}}
\newcommand{\PR}[1]{\mathrm{Pr}\big(#1\big)}
\newcommand{\Tr}{\mathrm{Tr}}
\newcommand{\InR}[1]{\left\{ #1_R \right\}_{R\in \sigma}}

@@

@@

In the first order language $FO[\sigma]$ with signature $\sigma$ 
formulas are formed by variables $x_1,\dots,$ $x_i,\dots$,
the relation symbols in $\sigma$, the equal symbol $=$,
the usual Boolean connectives $\neg, \wedge, \vee, \dots$, 
the existential and universal quantifiers $\exists, \forall$, and
the parentheses $),($. Then formulas in $FO[\sigma]$ are defined as 
follows.
\vspace*{-0.2em}
\begin{itemize}[topsep=1pt, itemsep=1pt]
	\item The expression $R(y_1,\dots,y_a)$, where the $y_i$'s are variables and $R$
	is a relation symbol in $\sigma$ such that $ar(R)=a$,
	belongs to $FO[\sigma]$.
	\item The expression $y_1=y_2$, where $y_1, y_2$ are variables, 
	belongs to $FO[\sigma]$.
	\item Given formulas $\phi, \psi \in FO[\sigma]$, any Boolean combination of them
	$\neg(\phi), (\phi \wedge \psi), (\phi \vee \psi), \dots$ belongs to $FO[\sigma]$ as well.
	\item Given a formula $\phi \in FO[\sigma]$ and $x$ a variable that 
	does not appear bounded
	by a quantifier in $\phi$, the expressions $\forall x (\phi)$ and 
	$\exists x (\phi)$ belong both to $FO[\sigma]$. 
\end{itemize}  
We will write $\forall y_1, y_2,\dots, y_m$ or simply $\forall \overline{y}$
instead of  
$\forall y_1, \forall y_2,\dots, \forall y_m$ and likewise for
the quantifier $\exists$. Also, if $\overline{y}:=(y_1,\dots,y_a)$ is a
tuple of variables we may write simply $R(\overline{y})$ instead
of $R(y_1\dots,y_a)$.\par
For the remaining of this article we will reserve the names $x,y,z$
for the variables in our first order formulas.\par
We define the set of free variables of a formula as usual. 
Given a formula $\phi\in FO[\sigma]$ we will use the notation $\phi(\overline{y})$ 
to denote that $\overline{y}$ is a tuple of 
(different) variables that contains all free variables in $\phi$ and
none of its bounded variables, although it may contain variables
which not appear in $\phi$. \par
Formulas with no free variables are called sentences and 
formulas with no quantifiers are called open formulas. \par
The quantifier rank of a formula $\phi$, denoted by $qr(\phi)$, 
is defined as the maximum number of nested quantifiers in $\phi$. \par
Sentences in $FO[\sigma]$ are interpreted over $\sigma$-structures
in the natural way. Given an structure $\mathcal{A}$, and a sentence
$\phi\in FO[\sigma]$ we write $\mathcal{A} \models \phi$ to denote 
that $\mathcal{A}$ satisfies $\phi$. If $\psi(\overline{y})$ is a
formula, $\overline{a}$ are elements in the universe of 
$\mathcal{A}$, and $\overline{y}$ and $\overline{a}$ are lists of the same size,
then we write $\mathcal{A} \models 
\psi(\overline{a})$
to mean that $\mathcal{A}$ satisfies $\psi$ when the free variables in
$\overline{y}$ are interpreted as the elements in $\overline{a}$ (i.e., 
the $i$-th element of $\overline{y}$ is interpreted as the $i$-th
element of $\overline{a}$).
\todo[inline]{Deber\'a al menos mencionar un par de trabajos que estudien random k-SAT y propiedades a.a.s suficientes para no-satisfacibilidad}

@@

For the rest of the article consider fixed:
\begin{itemize}
	\item A relational vocabulary $\sigma$ such that all the relations $R\in\sigma$ satisfy $ar(R)\geq 2$. 
	\item 
	Groups $\overline{\Phi}=\{ \Phi_R \}_{R\in \sigma}$
	such that each $\Phi_R$ is consists of 
	permutations on $[ar(R)]$ with the usual 
	composition as its operation.	
	\item 
	Sets $\{P_R\}_{R\in \sigma}$ satisfying that for 
	all $R\in \sigma$, 
	$P_R\subseteq \binom{[ar(R)]}{2}$

@@

\subsection{Colored Hypergraphs and Copies.}

\begin{definition}
	Let $\Sigma$ be a set. A \textbf{$\Sigma$-hypergraph}
	is a pair $(G, \chi)$ where $G$ is an hypergraph
	and $\chi: V(G)\rightarrow \Sigma$ is a map 
	called \textbf{$\Sigma$-coloring} of $G$. \par
	Given two $\Sigma$-hypergraphs $(G^1,\chi_1)$
	and $(G^2,\chi_2)$, and \textbf{isomorphism} between them is
	a bijection $f:V(G^1)\rightarrow V(G^2)$ satisfying
	that $f$ is an hypergraph isomorphism between $G^1$ and
	$G^2$ as well as
	$\chi_2(f(v))=\chi_1(v)$ for all $v\in V(G^1)$.\par	 
	Given a $\Sigma$-hypergraph $(G,\chi)$, an \textbf{automorphism}
	of $(G,\chi)$ is an isomorphism from it into itself. We will denote
	by $Aut(G,\chi)$ the group of such automorphisms. 
\end{definition}

@@

Let $G^1$ and $G^2$ be hypergraphs, and let
$V_1:=V(G^1), V_2:=V(G^2)$.
Let $\overline{v} \in V_1^*, 
\overline{u} \in V_2^*$ be tuples of the same length.
We say that $\overline{v}$ and $\overline{u}$ have
$k$-\textbf{similar} $r$-neighborhoods, written as
$(G^1,\overline{v})\simeq_{k,r}(G^2 \overline{u})$, if Duplicator wins
$d\ehr_k\big(N(\overline{v};r),
\overline{v};\, N(\overline{u};r),\overline{u}\big)$.
Given sets of vertices $X\subseteq V_1$ and $Y\subseteq V_2$
we say that $X$ and $Y$ have $k$-similar
$r$-neighborhoods, written as
$X\simeq_{k,r} Y$, if we can order their elements to form
lists $\overline{v}$, resp. $\overline{u}$ such that 
$(G^1,\overline{v})\simeq_{k,r}(G^2,\overline{u})$. 
Given sets of vertices $X\in V_1$, $Y\in V_2$ and 
tuples of the same length $\overline{v}\in V_1^*$ and
$\overline{u}\in V_2^*$ we will say that $(X,\overline{v})$ 
and $(Y,\overline{u})$ have $k$-similar $r$-neighborhoods,
written as $\big(G_1, (X,\overline{v})  \big)
\simeq_{k,r} \big(G_2, (Y,\overline{u})  \big)$, if
the elements of $X$ and $Y$ can be ordered in lists
$\overline{w}$, $\overline{z}$ such that
$(G_1,\overline{w}^\smallfrown \overline{v})
\simeq_{k,r} (G_2,\overline{z}^\smallfrown \overline{u})$. \par
Fix $r\in \N$. Suppose that $X\subseteq V_1$ and 
$Y\subseteq V_2$ can
be partitioned into sets $X=X_1\cup \dots \cup X_a$
and $Y=Y_1\cup \dots \cup Y_b$ 
such that $N(X_i;r)$'s, and the
$N(Y_i;r)$'s, are connected and disjoint. 
We say that $X$ and
$Y$ have $k$-\textbf{agreeable} $r$-neighborhoods,
written as $(G^1,X)\cong_{k,r} (G^2,Y)$, 
if for any set $Z\subset V_\delta$, with $\delta\in \{1,2\}$,
among the $X_i$'s or the $Y_i$'s
it is satisfied that ``the number of $X_i$'s  
such that $(G^\delta, Z) \simeq_{k,r} (G^1,X_i)$ 
and the number of $Y_i$'s such that
$(G^\delta,Z)\simeq_{k,r} (G^2,Y_i)$
are both equal or are both greater 
or equal than $k$" .

@@

\begin{proof}[Proof of \cref{ThmDuplicator}]
	%Set 
	%$\overline{v}[i]:=v_1,\dots,v_i$ and
	%$\overline{u}[i]:=u_1,\dots,u_i$
	%We say that Duplicator can play following the strategy $S$
	%if they can play in a way that
	%at the end of the $s$-th round, $\overline{w}[s]$ and
	%$\overline{z}[s]$ have $(k-s)$-similar $r_{k-s}$-neighborhoods.
	%In particular this means that at the end of the $k$-th
	%round Duplicator will have won $\ehr_k(G^1,G^2)$.	
	Let $X_1,\dots,X_a$ and 
	$Y_1,\dots,Y_b$ be partitions of 
	$X$ and $Y$ respectively
	as in the definition of $k$-agreeability.
	Define $r_0=(3^k-1)/2$ and $r_i=(r_{i-1}-1)/3$ for each
	$1\leq i \leq k$. 
	Let us denote by $v^1_i$ and $v^2_i$ the vertices played
	in $G^1$ and $G^2$ respectively during the $i$-th
	round of $\ehr_k(G^1,G^2)$. 
	We will show a winning strategy for Duplicator
	in $d\ehr_{k}\big(G^1;\, G^2\big)$. For each $0\leq i \leq k$,
	Duplicator will	keep track of some marked sets 
	of vertices $T\subset V_1$, $S\subset V_2$. 
	For $\delta=1,2$ each marked set
	$T\subset V_\delta$ will have associated a tuple
	of vertices $\overline{v}(T)\in V_\delta^*$ consisting
	of the vertices played in $G_2$ so far, ordered according
	to the rounds they where played, that were 
	"appropriately close" to $T$ when chosen.
	The game will start with no sets of vertices marked and 
	at the end of the $i$-th
	round Duplicator will perform one of the two
	following operations:
	\begin{itemize}
	\item Mark two sets $S\subset V_1$ and $T\subset V_2$ and
	define $\overline{v}(S)=v^1_i$ and $\overline{v}(T)=v^2_i$.
	\item Given two sets $S\subset V_1$, $T\subset V_2$ that were 
	previously marked during the same round, append $v^1_i$
	and $v^2_i$ to $\overline{v}(S)$ and $\overline{v}(T)$ 
	respectively. 
	\end{itemize}
	In particular this means that at the 
	end of the $i$-th round the marked sets $S\subset V_1$
	, $T\subset V_2$ and their respective lists $\overline{v}(S)$,
	$\overline{v}(T)$ satisfy
	\begin{itemize}
		\item[(i)] For $\delta=1,2$, each vertex played
		so far $v^\delta_j\in V_\delta$ belongs to 
		$\overline{v}(S)$ for a	 unique marked set 
		$S\subset V_\delta$.
		\item[(ii)] Let $S\subset V_1$ and $T\subset V_2$ be sets
		marked during the same round. Then any previously played
		vertex $v^1_j$ occupies a position in $\overline{v}(S)$
		if and only if $v^2_j$ occupies the same position 
		in $\overline{v}(T)$.
	\end{itemize}
	The following conditions will also be satisfied at the 
	end of the $i$-th round
	\begin{itemize}
		\item[(iii)] 
			\begin{itemize}
			\item  Let $S\subset V_1$ be a marked set. Then 
			for any different marked $S^\prime \subset V_1$ 
			of any different $S^\prime$ among $X_1,\dots,X_a$
			it holds $d(S,S^\prime)>2r_i + 1$. 
			\item Let $T\subset V_2$ be a marked set. Then
			for any different marked $T^\prime \subset V_2$
			or any different $T^\prime$ among
			$Y_1,\dots, Y_b$  it holds $d(T,T^\prime)>2r_i +1$.
			\end{itemize}
		\item[(iv)] Let $S\subset V_1, T\subset V_2$ be sets
		marked during the same round. Then
		\[
		\big(G^1, (S,\overline{v}(S))\big)\simeq_{k-i,r_i}
		\big(G^2, (T,\overline{v}(T))\big).	\]

@@

\subsection{Types of trees}

We define tree $T$ as a connected hypergraph such that
$ex(T)=-1$. We define a vertex-rooted tree $(T,v)$ 
as a tree $T$ with a 
distinguished vertex $v\in V(T)$ called its root. We will
usually omit the root when it is not relevant and 
write just $T$ instead of $(T,v)$. We define the set
of initial edges of a vertex-rooted tree $(T,v)$ as the
set of edges in $T$ that contain $v$. \par
%
%Similarly, we define an edge-rooted tree $(T,e,v)$
%as a tree $T$ with a distinguished edge $e\in E(T)$ and
%a distinguished vertex $v\in e$. \par
Given a rooted tree $(T, v)$, and a vertex $u\in V(T)$, 
we define $\tau_{(T,v)}(u)$ as the tree $T[X]$ induced on the
set $X:=\{ \, w\in V(T) \, | \, d(v,w)=d(v,u)+ d(u,w) \,  \}
$, to which we assign $u$ as the root.
That is, $\tau_{(T,v)}(u)$ is the tree consisting of those vertices
whose only path to $v$ contains $u$.
\par
We define the radius of a vertex-rooted, or edge-rooted,
tree as the maximum distance between its marked
vertex and any other one. \par

Fix a natural number $k$. We will define 
two equivalence relations, one between 
rooted trees and another between pairs
$(T,e)$ of rooted trees $T$ and initial edges
$e\in E(T)$. We will name both relations
$k$-equivalence relations and
denote them by $\morph{k}$. 
They are defined recursively as follows:

\begin{itemize}
	\item Any two trees with radius zero are $k$-equivalent.
	Notice that those trees
	consist only of one vertex: their respective roots.
	\item Suppose that the $k$-equivalence relation has been
	defined for rooted trees with radius at most $r$. Let $\Sigma_r$
	be the set consisting of the root symbol $\tau$ and
	the $k$-equivalence classes of trees with radius lesser than $r$.
	Given a rooted tree $(T,v)$ with whose radius is lesser than $r$
	we define its canonical $\Sigma_r$-coloring as the map 
	$\chi_{(T,v)}: V(T)\rightarrow \Sigma_r$ satisfying that
	$\chi_{(T,v)}(u)$ is the $k$-equivalence class of $\mathrm{Tr}(u,T;v)$
	for any $u\neq v$ and $\chi_{(T,v)}(v)=\tau$. \par
	Let $T_1$ and $T_2$ be rooted trees with radius
	at most $r+1$. We say that $(T_1,v_1)\simeq_k (T_2,v_2)$ 
	if given any $\Sigma_r$-pattern $(e,\chi)$ the 
	"quantity of initial edges $e_1\prime\in E(T_1)$ such that
	$(e,\chi)\simeq (e_1,\chi_{(T_1,v_1)})$" and the
	"quantity of initial edges $e_2\prime\in E(T_2)$ such that
	$(e,\chi)\simeq (e_2,\chi_{(T_2,v_2)})$" are the same or
	are both greater than $k-1$.
\end{itemize}

We want prove the following
\begin{theorem} \label{thm:equivalenttrees} 
	Let $(T_1,v_1)$ and $(T_2,v_2)$ be rooted trees.
	Then, if they are $k$-equivalent Duplicator wins
	$d\ehr_{k}(T_1,v_1,T_2,v_2)$.
\end{theorem}

>>>>

\newcommand{\cc}{\mathfrak{c}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Hc}{\mathcal{H}}
\newcommand{\Lan}{\mathcal{L}}
\newcommand{\Ln}{\lim\limits_{n\to \infty}}
\newcommand{\clist}{\mathfrak{c}_{1}, \cdots, \mathfrak{c}_m}
\newcommand{\morph}[1]{\sim_#1}
\newcommand{\vlst}[2]{#1_1,\dots, #1_{#2}}
\newcommand{\gnp}{G(n,\beta_1/n^{a_1-1}, \dots,\beta_l/n^{a_l-1})}
\newcommand{\overbar}[1]{\mkern 1.5mu\overline{\mkern-1.5mu#1\mkern-1.5mu}\mkern 1.5mu}
\newcommand{\ehr}{\textsc{Ehr}}
\newcommand{\PR}[1]{\mathrm{Pr}\big(#1\big)}
\newcommand{\Tr}{\mathrm{Tr}}
\newcommand{\InR}[1]{\left\{ #1_R \right\}_{R\in \sigma}}

@@

\todo[inline]{Añadir referencias y trabajo relacionado con random SAT}

@@

In the first order language $FO[\sigma]$ with signature $\sigma$ 
formulas are formed by variables $x_1,\dots,$ $x_i,\dots$,
the relation symbols in $\sigma$, the equal symbol $=$,
the usual Boolean connectives $\neg, \wedge, \vee, \dots$, 
the existential and universal quantifiers $\exists, \forall$, and
the parentheses $),($. Then formulas in $FO[\sigma]$ are defined as 
follows.
\vspace*{-0.2em}
\begin{itemize}[topsep=1pt, itemsep=1pt]
	\item The expression $R(y_1,\dots,y_a)$, where the $y_i$'s are variables and $R$
	is a relation symbol in $\sigma$ such that $ar(R)=a$,
	belongs to $FO[\sigma]$.
	\item The expression $y_1=y_2$, where $y_1, y_2$ are variables, 
	belongs to $FO[\sigma]$.
	\item Given formulas $\phi, \psi \in FO[\sigma]$, any Boolean combination of them
	$\neg(\phi), (\phi \wedge \psi), (\phi \vee \psi), \dots$ belongs to $FO[\sigma]$ as well.
	\item Given a formula $\phi \in FO[\sigma]$ and $x$ a variable that 
	does not appear bounded
	by a quantifier in $\phi$, the expressions $\forall x (\phi)$ and 
	$\exists x (\phi)$ belong both to $FO[\sigma]$. 
\end{itemize}  
We will write $\forall y_1, y_2,\dots, y_m$ or simply $\forall \overline{y}$
instead of  
$\forall y_1, \forall y_2,\dots, \forall y_m$ and likewise for
the quantifier $\exists$. Also, if $\overline{y}:=(y_1,\dots,y_a)$ is a
tuple of variables we may write simply $R(\overline{y})$ instead
of $R(y_1\dots,y_a)$.\par
For the remaining of this article we will reserve the names $x,y,z$
for the variables in our first order formulas.\par
We define the set of free variables of a formula as usual. 
Given a formula $\phi\in FO[\sigma]$ we will use the notation $\phi(\overline{y})$ 
to denote that $\overline{y}$ is a tuple of 
(different) variables that contains all free variables in $\phi$ and
none of its bounded variables, although it may contain variables
which not appear in $\phi$. \par
Formulas with no free variables are called sentences and 
formulas with no quantifiers are called open formulas. \par
The quantifier rank of a formula $\phi$, denoted by $qr(\phi)$, 
is defined as the maximum number of nested quantifiers in $\phi$. \par
Sentences in $FO[\sigma]$ are interpreted over $\sigma$-structures
in the natural way. Given an structure $\mathcal{A}$, and a sentence
$\phi\in FO[\sigma]$ we write $\mathcal{A} \models \phi$ to denote 
that $\mathcal{A}$ satisfies $\phi$. If $\psi(\overline{y})$ is a
formula, $\overline{a}$ are elements in the universe of 
$\mathcal{A}$, and $\overline{y}$ and $\overline{a}$ are lists of the same size,
then we write $\mathcal{A} \models 
\psi(\overline{a})$
to mean that $\mathcal{A}$ satisfies $\psi$ when the free variables in
$\overline{y}$ are interpreted as the elements in $\overline{a}$ (i.e., 
the $i$-th element of $\overline{y}$ is interpreted as the $i$-th
element of $\overline{a}$).

@@

For the rest of the article consider fixed:
\begin{itemize}
	\item A relational vocabulary $\sigma$ such that all the relations $R\in\sigma$ satisfy $ar(R)\geq 2$. 
	\item 
	Groups $\{ \Phi_R \}_{R\in \sigma}$
	such that each $\Phi_R$ is consists of 
	permutations on $[ar(R)]$ with the usual 
	composition as its operation.	
	\item 
	Sets $\{P_R\}_{R\in \sigma}$ satisfying that for 
	all $R\in \sigma$, 
	$P_R\subseteq \binom{[ar(R)]}{2}$

@@

\subsection{Copies of Hypergraphs}

Given two hypergraphs $H_1, H_2$ an \textbf{isomorphism} 
$f$ between them is a bijection $f: V(H_1)\rightarrow V(H_2)$
such that for any $R\in \sigma$, a tuple $\overline{v}\in V(H_1)^*$
forms an edge $[\overline{v}]\in E_\sigma(H_1)$ if and only
if $[f(\overline{v})]\in E_\sigma(H_2)$. We say that $H_1$ and
$H_2$ are isomorphic, written as $H_1\simeq H_2$, if there exists
some isomorphism between them.\par

Let $H$ be an hypergraph. An \textbf{automorphism} of $H$
is an isomorphism from $H$ to itself. We will denote by
$Aut(H)$ the group of such automorphisms. \par

Let $H^\simeq$ be an isomorphism class of hypergraphs. Let
$H\in H^\simeq$ be a representative of the class. 
Then we define $ex(H^\simeq)$ as $ex(H)$. Clearly this definition
does not depend on the choice of $H$. The expressions
$|Aut(H^\simeq)|$,
$|V(H^\simeq)|$, $|E(H^\simeq)|$ or
$|E_R(H^\simeq)|$ for $R\in \sigma$ are defined 
in an analogous way.\par

Let $H$ be an hypergraph and let $V$ be a set. We define the
set $Copies(H,V)$ as the set of hypergraphs $H^\prime$ such that
$V(H^\prime)\subset V$ and $H\simeq H^\prime$. Analogously, if
$H^\simeq$ is an isomorphism class of hypergraphs we define
$Copies(H^\simeq,V)$ as the set of hypergraphs $H^\prime$ 
that satisfy
$V(H^\prime)\subset V$ as well as $H^\prime \in H^\simeq$.   \par

In our proofs it will be useful to consider colorings over 
hypergraphs as a way to assign extra information to their 
vertices.

\begin{definition}
	Let $\Sigma$ be a set. A \textbf{$\Sigma$-hypergraph}
	is a pair $(H, \chi)$ where $H$ is an hypergraph
	and $\chi: V(H)\rightarrow \Sigma$ is a map 
	called \textbf{$\Sigma$-coloring} of $H$.
\end{definition}

	Given two $\Sigma$-hypergraphs $(H_1,\chi_1)$
	and $(H_2,\chi_2)$, an \textbf{isomorphism} between them is
	a bijection $f:V(H_1)\rightarrow V(H_2)$ satisfying
	that $f$ is an hypergraph isomorphism between $H_1$ and
	$H_2$ as well as $\chi_2(f(v))=\chi_1(v)$ for all $v\in V(H_1)$.
	We say that $(H_1,\chi_1)$ is isomorphic to $(H_2,\chi_2)$,
	written as $(H_1, chi_1)\simeq (H_2,\chi_2)$, if there exists an
	isomorphism between them.
	\par	 
	Let $(H,\chi)$ be a $\Sigma$-hypergraph, an 
	\textbf{automorphism} of $(H,\chi)$ is an 
	isomorphism from it into itself. We will denote
	by $Aut(H,\chi)$ the group of such automorphisms. 
	\par
	As with the case of hypergraphs, if $H^\simeq$ is 
	an isomorphism class of $\Sigma$-hypergraphs
	then the expressions $|Aut(H^\simeq)|$ and
	$|V(H^\simeq)|$ are defined via representatives. \par
	Let $(H,\chi)$ be a $\Sigma$-hypergraph and let $V$ be a set.
	We define the set $Copies\big(
	(H,\chi),\, \, V\big)$ as the set of $\Sigma$-hypergraphs
	$(H^\prime,\chi^\prime)$ satisfying $V(H^\prime)\subset V$ and
	$(H,\chi)\simeq (H^\prime,\chi^\prime)$. Let $H^\simeq$ be 
	an isomorphism class of $\Sigma$-hypergraphs. Then the set
	$Copies(H^\simeq, V)$ is defined$\Sigma$-hypergraphs
	$(H^\prime,\chi^\prime)$ such that 
	$V(H^\prime)\subset V$ and
	$(H^\prime,\chi^\prime)\in H^\simeq$. 
	Let $v\in V$ and $s\in \Sigma$. We define the
	set $Copies\big(H^\simeq, V;\,\, (v,s)\big)$ 
	as the set of $\Sigma$-hypergraphs
	$(H^\prime,\chi^\prime)\in Copies(H^\simeq, V)$
	that satisfy $v\in V(H^\prime)$ as well as
	$\chi^\prime(v)=s$.

@@

Let $G^1$ and $G^2$ be hypergraphs, and let
$V_1:=V(G^1), V_2:=V(G^2)$.
Let $\overline{v} \in V_1^*, 
\overline{u} \in V_2^*$ be tuples of the same length.
We say that $\overline{v}$ and $\overline{u}$ have
$k$-\textbf{similar} $r$-neighborhoods, written as
$(G^1,\overline{v})\simeq_{k,r}(G^2 \overline{u})$, if Duplicator wins
$d\ehr_k\big(N(\overline{v};r),
\overline{v};\, N(\overline{u};r),\overline{u}\big)$.
Given sets of vertices $X\subseteq V_1$ and $Y\subseteq V_2$
we say that $X$ and $Y$ have $k$-similar
$r$-neighborhoods, written as
$X\simeq_{k,r} Y$, if we can order their elements to form
lists $\overline{v}$, resp. $\overline{u}$ such that 
$(G^1,\overline{v})\simeq_{k,r}(G^2,\overline{u})$. 
Given sets of vertices $X\in V_1$, $Y\in V_2$ and 
tuples of the same length $\overline{v}\in V_1^*$ and
$\overline{u}\in V_2^*$ we will say that $(X,\overline{v})$ 
and $(Y,\overline{u})$ have $k$-similar $r$-neighborhoods,
written as $\big(G_1, (X,\overline{v})  \big)
\simeq_{k,r} \big(G_2, (Y,\overline{u})  \big)$, if
the elements of $X$ and $Y$ can be ordered in lists
$\overline{w}$, $\overline{z}$ such that
$(G_1,\overline{w}^\smallfrown \overline{v})
\simeq_{k,r} (G_2,\overline{z}^\smallfrown \overline{u})$. \par
Fix $r\in \N$. Suppose that $X\subseteq V_1$ and 
$Y\subseteq V_2$ can
be partitioned into sets $X=X_1\cup \dots \cup X_a$
and $Y=Y_1\cup \dots \cup Y_b$ 
such that $N(X_i;r)$'s, and the
$N(Y_i;r)$'s, are connected and disjoint. 
We say that $X$ and
$Y$ have $k$-\textbf{analogous} $r$-neighborhoods,
written as $(G^1,X)\cong_{k,r} (G^2,Y)$, 
if for any set $Z\subset V_\delta$, with $\delta\in \{1,2\}$,
among the $X_i$'s or the $Y_i$'s
it is satisfied that ``the number of $X_i$'s  
such that $(G^\delta, Z) \simeq_{k,r} (G^1,X_i)$ 
and the number of $Y_i$'s such that
$(G^\delta,Z)\simeq_{k,r} (G^2,Y_i)$
are both equal or are both greater 
or equal than $k$" .

@@

\begin{proof}[Proof of \cref{ThmDuplicator}]
	%Set 
	%$\overline{v}[i]:=v_1,\dots,v_i$ and
	%$\overline{u}[i]:=u_1,\dots,u_i$
	%We say that Duplicator can play following the strategy $S$
	%if they can play in a way that
	%at the end of the $s$-th round, $\overline{w}[s]$ and
	%$\overline{z}[s]$ have $(k-s)$-similar $r_{k-s}$-neighborhoods.
	%In particular this means that at the end of the $k$-th
	%round Duplicator will have won $\ehr_k(G^1,G^2)$.	
	Let $X_1,\dots,X_a$ and 
	$Y_1,\dots,Y_b$ be partitions of 
	$X$ and $Y$ respectively
	as in the definition of $\cong_{k,r}$.
	Define $r_0=(3^k-1)/2$ and $r_i=(r_{i-1}-1)/3$ for each
	$1\leq i \leq k$. 
	Let us denote by $v^1_i$ and $v^2_i$ the vertices played
	in $G^1$ and $G^2$ respectively during the $i$-th
	round of $\ehr_k(G^1,G^2)$. 
	We will show a winning strategy for Duplicator
	in $d\ehr_{k}\big(G^1;\, G^2\big)$. For each $0\leq i \leq k$,
	Duplicator will	keep track of some marked sets 
	of vertices $T\subset V_1$, $S\subset V_2$. 
	For $\delta=1,2$ each marked set
	$T\subset V_\delta$ will have associated a tuple
	of vertices $\overline{v}(T)\in V_\delta^*$ consisting
	of the vertices played in $G_2$ so far, ordered according
	to the rounds they where played, that were 
	"appropriately close" to $T$ when chosen.
	The game will start with no sets of vertices marked and 
	at the end of the $i$-th
	round Duplicator will perform one of the two
	following operations:
	\begin{itemize}
	\item Mark two sets $S\subset V_1$ and $T\subset V_2$ and
	define $\overline{v}(S)=v^1_i$ and $\overline{v}(T)=v^2_i$.
	\item Given two sets $S\subset V_1$, $T\subset V_2$ that were 
	previously marked during the same round, append $v^1_i$
	and $v^2_i$ to $\overline{v}(S)$ and $\overline{v}(T)$ 
	respectively. 
	\end{itemize}
	In particular this means that at the 
	end of the $i$-th round the marked sets $S\subset V_1$
	, $T\subset V_2$ and their respective lists $\overline{v}(S)$,
	$\overline{v}(T)$ satisfy
	\begin{itemize}
		\item[(i)] For $\delta=1,2$, each vertex played
		so far $v^\delta_j\in V_\delta$ belongs to 
		$\overline{v}(S)$ for a	 unique marked set 
		$S\subset V_\delta$.
		\item[(ii)] Let $S\subset V_1$ and $T\subset V_2$ be sets
		marked during the same round. Then any previously played
		vertex $v^1_j$ occupies a position in $\overline{v}(S)$
		if and only if $v^2_j$ occupies the same position 
		in $\overline{v}(T)$.
	\end{itemize}
	The following conditions will also be satisfied at the 
	end of the $i$-th round
	\begin{itemize}
		\item[(iii)] 
			\begin{itemize}
			\item  Let $S\subset V_1$ be a marked set. Then 
			for any different marked $S^\prime \subset V_1$ 
			of any different $S^\prime$ among $X_1,\dots,X_a$
			it holds $d(S,S^\prime)>2r_i + 1$. 
			\item Let $T\subset V_2$ be a marked set. Then
			for any different marked $T^\prime \subset V_2$
			or any different $T^\prime$ among
			$Y_1,\dots, Y_b$  it holds $d(T,T^\prime)>2r_i +1$.
			\end{itemize}
		\item[(iv)] Let $S\subset V_1, T\subset V_2$ be sets
		marked during the same round. Then
		\[
		\big(G^1, (S,\overline{v}(S))\big)\simeq_{k-i,r_i}
		\big(G^2, (T,\overline{v}(T))\big).	\]

@@

\subsection{k-Equivalence relation}

To prove \cref{thm:main} we are going to exploit the facts that
(1) for any fixed $r\in N$, $r$-neighborhoods in $G_n$ a.a.s 
are either trees of unicycles, and
(2) we can identify $k$-equivalent trees
and unicycles sufficiently often in a simple way.

\subsubsection{k-Equivalent trees}

\begin{definition}
	We define a \textbf{tree} $T$ as a connected hypergraph such that
	$ex(T)=-1$. A \textbf{rooted tree} $(T,v)$ is a tree $T$ with a 
	distinguished vertex $v\in V(T)$ called its \textbf{root}.
\end{definition}
We will usually omit the root when it is not relevant and 
write just $T$ instead of $(T,v)$. The
\textbf{initial edges} of a rooted tree $(T,v)$ are 
the edges in $T$ that contain $v$. \par

%
%Similarly, we define an edge-rooted tree $(T,e,v)$
%as a tree $T$ with a distinguished edge $e\in E(T)$ and
%a distinguished vertex $v\in e$. \par
Given a rooted tree $(T, v)$, and a vertex $u\in V(T)$, 
we define $\mathrm{Tr}(T,v;\,\, u)$ as the tree $T[X]$ induced on the
set $X:=\{ \, w\in V(T) \, | \, d(v,w)=d(v,u)+ d(u,w) \,  \}
$, to which we assign $u$ as the root.
That is, $\mathrm{Tr}(T,v;\,\, u)$ is the tree consisting of those vertices
whose only path to $v$ contains $u$.
\par
We define the radius of a rooted tree
as the maximum distance between its root
and any other vertex. \par

\begin{definition}

Fix a natural number $k$. We will define the
\textbf{$k$-equivalence} relation, written as 
$\sim_k$,  over rooted trees
inductively over their radii as follows:

\begin{itemize}
	\item Any two trees with radius zero are $k$-equivalent.
	Notice that those trees
	consist only of one vertex: their respective roots.

	\item Suppose that the $k$-equivalence relation has been
	defined for rooted trees with radius at most $r$. Let $\Sigma_r$
	be the set consisting of the root symbol $\rho$ and
	the $k$-equivalence classes of trees with radius at most $r$.
	Given a rooted tree $(T,v)$ with whose radius is $r+1$
	we define its canonical $\Sigma_r$-coloring as the map 
	$\tau_{(T,v)}: V(T)\rightarrow \Sigma_r$ satisfying that
	for any $u\neq v$ $\tau_{(T,v)}(u)$ is the $k$-equivalence class 
	of $\mathrm{Tr}(T,u;\, \,v)$ and that $\tau_{(T,v)}(v)=\tau$. \par
	Let $T_1$ and $T_2$ be rooted trees with radius $r+1$. 
	We say that $(T_1,v_1)\sim_k (T_2,v_2)$ 
	if for $\delta=1,2$, given any initial edge $e$ from $(T_\delta,v_\delta)$
	the
	``quantity of initial edges $e_1\in E(T_1)$ such that
	\[
	\big(e,\tau_{(T_\delta,v_\delta)}\big)
	\simeq \big(e_1,\tau_{(T_1,v_1)}\big)" 
	\] and the
	``quantity of initial edges $e_2\in E(T_2)$ such that
	\[
	\big(e,\tau_{(T_\delta,v_\delta)}\big)
	\simeq \big(e_2,\tau_{(T_2,v_2)}\big)"\] are equal or
	are both greater than $k-1$.
\end{itemize}

\begin{definition}
	Let $\Sigma_{(k,r-1)}$ be the set of $\sim_k$ classes
	of rooted trees with radii at most $r-1$. Then
	we call a $(k,r)$-\textbf{pattern} to an isomorphism class
	of $(\Sigma_{(k,r-1)}\cup \{\rho \})$-hypergraphs 
	$(e,\tau)$ consisting of only one edge that satisfy 
	$\tau(v)=\rho$ for exactly one vertex $v\in V(e)$. We will
	denote by $P(k,r)$ the set of $(k,r)$-patterns.
\end{definition}

The following is a way of characterizing $\sim_k$ classes
of rooted trees with radii at most $r$ that will be useful later.
